Cycle Route Uptake and Scenario Estimation (CRUSE): an approach for developing strategic cycle network planning tools

### 2024-03-25 paper.qmd
Mention cycle tourism layer

<!-- Mobility kills. -->
## Background

@@

However, travel to school and work only constitute 39% of all trips in Ireland, excluding 'returning home' trips, according to the 2022 National Household Travel Survey (NHTS) [@national2022].
To overcome this issue, we developed a spatial interaction modeling methodology to estimate the number of trips between each OD pair for additional trip purposes.
The classification of trip purposes used in the CRUSE Tool was guided mainly by the trip purpose classification found within the National Household Travel Survey (NHTS), but with the addition of categories based on the comprehensive POWSCAR data, and the need to include recreational trips and multi-stage trips. <!-- This is already implemented, right?--> 
An overview of the trip purposes used in CRUSE is presented in @fig-trip-purposes. <!--This should be Table 2--->

@@

Trip purposes used in the CRUSE Tool.
:::

@@

- Domestic with cycle trips starting at home
- Domestic trips involving travel by other mode to the start of the cycle trip
- Cycle tourism, where start and end trips are different
- Sport cycling 
-->
```
## Routing

@@

<!-- The results for the other -->
## Selected qualitative results {#sec-qualitative}

>>>>

<!-- Mobility kills. -->

## Background

@@

However, travel to school and work account for less than half (39%) of all trips in Ireland, excluding 'returning home' trips, according to the 2022 National Household Travel Survey (NHTS) [@national2022].
This represents a substantial decline in the proportion of trips covered by POWSCAR data compared with pre-COVID survey results, with 51% of non-return trips being for work or education according to the 2017 release of the same report [@national2017].
To tackle this issue, we developed a spatial interaction modeling methodology to estimate the number of trips between each OD pair for additional trip purposes.
The classification of trip purposes used in the CRUSE Tool was guided mainly by the trip purpose classification found within the National Household Travel Survey (NHTS), but with the addition of categories based on the comprehensive POWSCAR data, and the need to include recreational trips and multi-stage trips.
<!-- This is already implemented, right?--> An overview of the trip purposes used in CRUSE is presented in @fig-trip-purposes.
<!--This should be Table 2--->

@@

Everyday trip purposes used in the CRUSE Tool.
:::

@@

- Domestic with cycle trips starting at home
- Domestic trips involving travel by other mode to the start of the cycle trip
- Cycle tourism, where start and end trips are different
- Sport cycling 
-->
```
Following feedback from stakeholders, we added another, 'non-everyday' trip purpose in an extension phase: cycle tourism.
As outlined in the CRUSE Extension report [reference and link to be added on publication], this involved developing an inter-county spatial interaction model to estimate the number of trips between each county for cycle tourism, with trip attractors including campsites and major international transport hubs.

## Routing

@@

<!-- The results for the other -->

## Selected qualitative results {#sec-qualitative}

### 2024-03-25 paper.tex
Mention cycle tourism layer

However, travel to school and work only constitute 39\% of all trips in
Ireland, excluding `returning home' trips, according to the 2022
National Household Travel Survey (NHTS) \citep{national2022}. To
overcome this issue, we developed a spatial interaction modeling
methodology to estimate the number of trips between each OD pair for
additional trip purposes. The classification of trip purposes used in
the CRUSE Tool was guided mainly by the trip purpose classification
found within the National Household Travel Survey (NHTS), but with the
addition of categories based on the comprehensive POWSCAR data, and the
need to include recreational trips and multi-stage trips. An overview of
the trip purposes used in CRUSE is presented in
Figure~\ref{fig-trip-purposes}.

>>>>

However, travel to school and work account for less than half (39\%) of
all trips in Ireland, excluding `returning home' trips, according to the
2022 National Household Travel Survey (NHTS) \citep{national2022}. This
represents a substantial decline in the proportion of trips covered by
POWSCAR data compared with pre-COVID survey results, with 51\% of
non-return trips being for work or education according to the 2017
release of the same report \citep{national2017}. To tackle this issue,
we developed a spatial interaction modeling methodology to estimate the
number of trips between each OD pair for additional trip purposes. The
classification of trip purposes used in the CRUSE Tool was guided mainly
by the trip purpose classification found within the National Household
Travel Survey (NHTS), but with the addition of categories based on the
comprehensive POWSCAR data, and the need to include recreational trips
and multi-stage trips. An overview of the trip purposes used in CRUSE is
presented in Figure~\ref{fig-trip-purposes}.
